### 2019-09-16 draft.tex
adds conference facilities
add tikz

@@

\subsection{Conference Facilities}
\begin{itemize}
  \item \textbf{The Illini Union}\\
  \item \textbf{NCSA}
  \item \textbf{Engineering Hall}
  \item \textbf{The I-Hotel}
  \item \textbf{}
\end{itemize}

@@

>>>>

% Creates the flow chart for conference management
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows}

\tikzstyle{chair} = [rectangle, rounded corners, minimum width=2cm, minimum height=1cm,text centered, draw=black, fill=blue!30]
\tikzstyle{director} = [rectangle, rounded corners, minimum width=2cm, minimum height=1cm,text centered, draw=black, fill=green!30]
\tikzstyle{coordinator} = [rectangle, rounded corners, minimum width=2cm, minimum height=1cm,text centered, draw=black, fill=red!30]
\tikzstyle{arrow} = [thick,->,>=stealth]

@@

\subsection{Conference Facilities}
\begin{itemize}
  \item \textbf{The Illini Union}\\
  \item \textbf{National Center for Supercomputing Applications (NCSA)}\\
  \item \textbf{Engineering Hall}\\
  \item \textbf{The I-Hotel}\\
  \item \textbf{}\\
\end{itemize}

@@

\begin{tikzpicture}[node distance = 2cm]

  \node (gen chair) [chair] {General Co-Chair};
  \node (tech chair) [chair] {Technical Co-Chair};
  \node (fin dir) [director] {Financial Director};
  \node (pub dir) [director] {Communications Director};
  \node (reg coord) [coordinator] {Registration Coordinator};
  % \node (gen chair) [chair] {General Co-Chair};
  % \node (gen chair) [chair] {General Co-Chair};
  % \node (gen chair) [chair] {General Co-Chair};
  % \node (gen chair) [chair] {General Co-Chair};
  % \node (gen chair) [chair] {General Co-Chair};

\end{tikzpicture}
